The Concurrent Calculi Formalisation Benchmark

### 2023-10-10 paper/paper.tex

>>>>

As with the challenges that came before, this challenge is intended to
have useful solutions, but not to cover every problem that may be
faced when mechanised systems based on message passing calculi. Going
beyond the current challenges could be in one of two dimensions: the
first dimension about making harder challenges starting from the
current ones, and a second one about devising challenges not covered
by the current benchmarks.

The proposed challenges are orthogonal, however, in general systems
will combine some or all aspects of the challenges. An interesting
second round of formalisations could entail combining the features of
the challenges. In the following table we consider the following three
additions: First the addition of choice to the type level and the
process level. Second, the addition of recursion (and recursion types
for typed systems). And finally, the addition of channel delegation
for those calculi that do not already support it.

The following table shows which extension should be suitable (denoted
by a $+$) for each challenge:

\vspace{.5em}

\begin{tabular}{|r|c|c|c|}
  \hline
  & Linearity & \shortstack{Scope \\ extrusion} & Coinduction \\
  \hline
  Choice & $+$ & $+$  & $+$ \\
  \hline
  \shortstack{Recursive \\ types} & $+$  & $+$ & \\
  \hline
  Delegation & $+$ & & $+$ \\
  \hline
\end{tabular}

\vspace{.5em}

Note that these additions, make the challenges less orthogonal by
combining some of their features. This is to be expected, in the sense
that the proposed challenges should form the building blocks of more
complex systems.

The other dimension to extend these calculi corresponds to systems
that are not covered by our challenges\dots
% Multiparty session types, and choreographies.

% different notions of bisimilarity (barbed, or weak, etc.), trace equivalence.

% Exercising different features of proof assistants like: code
% extraction and/or code automation.

% Interaction between formalised proofs and model checkers.

% And any other
